The transiting dust clumps in the evolved disk of the Sun-like UXOr RZ~Psc

### 2016-08-31 ms.tex
updated to rsos format, whew

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\documentclass[useAMS,usenatbib,usegraphicx,referee]{mn2e}
\documentclass[useAMS,usenatbib,usegraphicx]{mn2e}
%\documentclass{emulateapj}
\usepackage{times,amssymb,hyperref,aas_macros}
\usepackage{comment}

@@

\author[Grant M. Kennedy et al]{Grant M. Kennedy\thanks{Email:
    \href{mailto:gkennedy@ast.cam.ac.uk}{gkennedy@ast.cam.ac.uk}}$^1$,
  Matthew A. Kenworthy$^2$,
  Joshua Pepper$^3$, \newauthor
  Joseph E. Rodriguez$^{4,5}$, 
  Robert J. Siverd$^6$, \&
  Keivan G. Stassun$^{5,7}$ \\
  $^1$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3
  0HA, UK \\
  $^2$ Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the
  Netherlands \\
  $^3$ Department of Physics, Lehigh University, 16 Memorial Drive East, Bethlehem, PA
  18015, USA \\
  $^4$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, MS-78, Cambridge, MA
  02138, USA \\
  $^5$ Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center,
  Nashville, TN 37235, USA \\
  $^6$ Las Cumbres Observatory Global Telescope Network, 6740 Cortona Dr., Suite 102, Santa
  Barbara, CA 93117, USA \\
  $^7$ Department of Physics, Fisk University, 1000 17th Avenue North, Nashville, TN
  37208, USA \\
}
\maketitle

@@

\begin{keywords}
  circumstellar matter, variable stars, protoplanetary disks, debris disks
\end{keywords}

@@

Disks of gas and dust surround essentially all young analogues of our Sun
\citep[e.g.][]{2001ApJ...553L.153H}. The lifetime of the gas in these disks is very short
compared to the stellar lifetime, and within a few million years most has accreted onto
the star and the remainder been lost to space in photoevaporative flows. The evolution of
the dust during this phase is uncertain, but the existence of gas giant planets makes it
clear that planetary building blocks, and of course some planets, form on a similar or
shorter timescale.

Beyond the first few million years a typical star hosts a planetary system, the
components being the planets themselves and a residual disk of small bodies. These
``planetesimals'' -- the asteroids and comets -- make up the ``debris disk'', where the
standard picture is that destructive collisions between them generate a size distribution
of fragments that extends down to micron-sized dust
\citep[e.g.][]{1993prpl.conf.1253B,2002MNRAS.334..589W,2010RAA....10..383K}.

The state of planetary systems as they emerge from the gas-rich phase is
uncertain. Planets' locations are not finalised at this epoch, but may move by
interacting with other stars, planets, and/or planetesimals in the system
\citep[e.g.][]{2007ApJ...669.1298F,1996Sci...274..954R,2005Natur.435..459T}. Similarly,
the state and origin of the debris disk is uncertain. At stellocentric distances near
1au, the region of interest in this article, it could be that dust observed at this time
is related to the final stages of planet formation
\citep[e.g.][]{2010ApJ...717L..57M,2012MNRAS.tmp.3462J}, originates in young analogues of
our Asteroid belt \citep{2013MNRAS.433.2334K}, is a signature of comets scattered inwards
from more distant regions \citep[e.g.][]{2009MNRAS.399..385B}, or is simply a remnant of
the gas-rich disk that has yet to be dispersed \citep{2014MNRAS.tmp...88K}. In the
absence of gas detections that argue for the latter scenario, discerning among these
various scenarios, which are not mutually exclusive, is difficult.

A promising way to probe these inner regions is by observing temporal variability
\citep[e.g.][]{2014Sci...345.1032M}. Optical and IR stellar variation has been studied
for decades \citep[e.g.][]{1945ApJ...102..168J,1994AJ....108.1906H}, and has recently
been reinvigorated by large scale efforts
\citep[e.g.][]{2011ApJ...733...50M,2014AJ....147...82C} and as a side-effect of
large-scale surveys for transiting planets
\citep{2012AJ....143...72M,2013AJ....146..112R,2016MNRAS.457.3988B}. Of many different
classes of variables, the ones of most interest and relevance here are the
``UXOrs''. These are usually Herbig Ae/Be stars, and typically show several magnitudes of
extinction that is generally attributed to variable obscuration by circumstellar dust
\citep{1994AJ....108.1906H,1999AJ....118.1043H,2000A&A...364..633N}.\footnote{Not all
  stars occulted by dust are UXOrs. Two main classes are: those occulted by circumstellar
  material beyond $\gtrsim$10au, such as AA~Tau and V409~Tau which show
  $\gtrsim$year-long dimming events \citep{2013A&A...557A..77B,2015AJ....150...32R}, and
  systems such as $\epsilon$~Aur, J1407, EE~Cep, and OGLE-LMC-ECL-11893 where the
  occultations are attributed to circumsecondary disks
  \citep[e.g.][]{1999MNRAS.303..521M,2012AJ....143...72M,2014ApJ...788...41D,2015ApJS..220...14K}.}
Two key arguments that favour circumstellar dust as the cause are i) ``blueing'', where
the star is reddened when moderately dimmed but returns to the stellar colour for very
deep ($\gtrsim$1mag) events -- the remaining flux is interpreted as light scattered off
circumstellar dust \citep{1988SvAL...14...27G}, and ii) increased polarisation fraction
during dimming events, caused by a greater fraction of the flux being contributed by
dust-scattered light \citep[e.g.][]{2001ARep...45...51R}. UXOrs therefore reveal
information on the degree of non-axisymmetry, the ``clumpiness'', of dust orbiting a star
on spatial scales similar to the star itself. The observations can span multiple orbits
to test for repeated dimming events \citep[e.g.][]{1999A&A...349..619B}, and by using
different bandpasses and polarisation can estimate dust grain sizes
\citep[e.g.][]{1988SvAL...14...27G,1994ASPC...62...63G}.

In the majority of UXOr-like cases (i.e. those related to obscuration by dust), including
other classes such as ``dippers''
\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A}, the processes causing young
stars to vary are attributed to gas-rich protoplanetary disks. For Herbig Ae/Be stars the
obscuration is thought to be caused by hydrodynamic turbulence that lifts dust above the
puffed up inner rim of a self-shadowed disk \citep{2003ApJ...594L..47D}. For the dippers,
which are observed around low-mass stars, the obscuration is attributed to dust in
accretion streams that link the inner disk and the stellar surface, and/or to variations
in the height of the inner disk edge
\citep{1999A&A...349..619B,2016ApJ...816...69A,2016arXiv160503985B}. The common theme is
therefore that the location of the occulting dust is as close to the star as physically
possible, being set by sublimation. These systems tell us about the nature of turbulence
and accretion in gas-dominated disks, but so far reveal little about how these disks
transition to the debris phase and the subsequent evolution.

Here we focus on RZ~Psc, a star that shows UXOr-like variability
\citep[e.g.][]{1985PZ.....22..181Z,1999A&AS..140..293G,2003ARep...47..580S}. As a young
K0V type star with no evidence for gas accretion, but a strong infrared (IR) excess
suggestive of an Asteroid belt analogue, this system appears unique among UXOrs and may
provide new information on the structure of inner planetary systems following dispersal
of the gas disk \citep{2010A&A...524A...8G,2013A&A...553L...1D}. Specifically, we use a
decade of ground-based optical photometry of RZ~Psc (section \ref{s:data}) to draw
conclusions on dust location (section \ref{s:where}), and discuss the possible disk
structure and evolutionary state in section \ref{s:disk}. We conclude in section
\ref{s:conc}.

@@

There is significant evidence that the optical variations seen towards RZ~Psc are caused
by circumstellar dust: i) during dimming events the colour becomes redder
\citep{1985PZ.....22..181Z,1980PZ.....21..310K} in a way consistent with that expected
for dust \citep{1981Afz....17...87P,2004ARep...48..470P}, ii) the maximum depth is about
2.5mag and during these events the colour returns to near stellar values, suggesting that
the remaining emission is from light scattered off the circumstellar dust \citep[i.e. the
star is fully occulted,][]{1981Afz....17...87P,1988SvAL...14...27G}, and iii) the
polarisation fraction increases during the transits, as expected if an increasing
fraction of the light is scattered off circumstellar dust
\citep{1988SvAL...14...27G,1991Afz....34..333K,2003ARep...47..580S}.

What separates RZ~Psc from other UXOrs (and dippers) is i) the spectral type is K0V
rather than Herbig Ae/Be for UXOrs and M-type for dippers, ii) the occulting dust lies
well beyond the sublimation radius, and iii) the star is not associated with a
star-forming region so is inferred to be a few tens of millions of years old. The dust
distance has been inferred from the speed of ingress of dimming events, which was
previously estimated as about 0.6au \citep[for circular
orbits,][]{2013A&A...553L...1D}. Corroborating evidence comes from the $\sim$500K
temperature of the dust seen in the mid-IR, which places it near 0.4-0.7au (depending on
optical depth) and therefore at a location consistent with the occulting dust
\citep{2013A&A...553L...1D}. The distance to RZ~Psc is unknown, but as an apparently
isolated star that shows Li absorption the age has been estimated as a few tens of Myr,
and therefore beyond the age at which a gas-rich disk should exist
\citep{2010A&A...524A...8G,2014A&A...563A.139P}. Further distinguishing features are that
the duration of the dimming events is relatively short compared to other UXOrs, a few
days rather than a few weeks, and that no near-IR excess or accretion signatures are seen
\citep{2014A&A...563A.139P}, so interpretations related to accretion of disk material
onto the star \citep[e.g.][]{1999AJ....118.1043H,1999A&A...349..619B,2016arXiv160503985B}
are unlikely.

Thus, the potentially compelling and unique aspect for RZ~Psc is that we are observing
dimming events from dust in a main-sequence planetary system that resides at about
0.5au. This dust is also seen in thermal emission, so deriving joint constraints on the
dust properties and structure may be possible. As argued by \citet{2013A&A...553L...1D} a
picture is emerging in which RZ~Psc is surrounded by a massive young version of our own
asteroid belt, in which planetesimals are continually being destroyed. These collisions
generate the large collective surface area of small dust that emits strongly in the
mid-IR, and the system geometry means that this dust also sometimes passes in front of
the star.

Given an interpretation related to individual planetesimal disruptions, rather than
hydrodynamics, it is perhaps surprising that to date the dimming events are not seen to
be periodic \citep{1999AstL...25..243R,2013A&A...553L...1D}. The only cyclical variation
seen in light curves for RZ~Psc is a 12.4 year variation with an amplitude of 0.5 mag,
which is attributed to either a magnetic cycle, or precession of an otherwise unseen
outer disk due to perturbations from an unseen companion \citep{2013A&A...553L...1D}.

@@

To study the temporal variability of RZ~Psc we use two seasons of public data from the
Wide-Angle Search for Planets \citep[WASP,][]{2006PASP..118.1407P}, and nine seasons of
data from the Kilodegree Extremely Little Telescope North
\citep[KELT-North,][]{2007PASP..119..923P}. We also collected, but ultimately did not
use, photometric observations of RZ~Psc from a wide variety of other sources \citep[][,
the Catalina Sky Survey, the American Association of Variable Star Observers, the All-Sky
Automated
Survey]{1994AJ....108.1906H,1973IBVS..783....1K,1980PZ.....21..310K,1985PZ.....22..181Z,1991Afz....34..333K,1997AcA....47..467P,2014Ap.....57..491P}. Most
of these other data have been previously published and their collation here is largely
for the benefit of others. This compilation contains nearly all data for which tables
have been published, but aside from the Harvard plate photometry published by
\citet{1999A&AS..140..293G} we have not sought other photometry so the light curve
remains incomplete.\footnote{Normalised photometry is available at
  \href{https://github.com/drgmk/rzpsc}{https://github.com/drgmk/rzpsc}}

Here we focus on the WASP and KELT-North data, as it has not been previously analysed and
has considerably higher cadence (many measurements per night) and temporal coverage
(nightly, weather permitting) than other data sets. The WASP data from 2004 and 2006 are
public and were obtained from an online
archive\footnote{\href{http://wasp.cerit-sc.cz}{http://wasp.cerit-sc.cz}}. These data
were processed in a manner similar to that described by \citet{2014MNRAS.441.2845V},
where common-mode variations were removed using 50 quiet nearby stars. The KELT-North
data, 2006-2014, were used in raw form, the only specific treatment being a 4\% relative
correction being made to ensure observations taken in the ``east'' and ``west'' telescope
orientations have the same calibration. For a full description of the KELT-North data
reduction, see \citet{2012ApJ...761..123S}.

@@

Nevertheless, Figure \ref{fig:waspkeltzoom} shows an unprecedented view of dimming events
seen towards RZ~Psc, and that key information on the ingress and egress of dimming events
is present. The dimming rate is such that it can be resolved temporally, and hence the
velocity and radial location of the dust clumps estimated. While such estimates have been
made in the past based on one or two individual events \citep{1985PZ.....22..181Z}, these
data make them possible for an ensemble of tens of events.

@@

% period-search.pro
\begin{figure}
\begin{center}
\hspace{-0.5cm} \includegraphics[width=0.5\textwidth]{figs/auto.eps}
\caption{Discrete autocorrelation function for yearly WASP and KELT-North data, computed for
  lags between 10-155 days). The second and third lines from the top show all data, and
  2006-excluded data. Squares show points more than 3$\sigma$ from the sigma-clipped
  mean. The topmost line shows the number of years that show a peak (square) within each
  5 day bin. The peak at 70 days is 7 years and the dashed line is zero.}\label{fig:auto}
\end{center}
\end{figure}

We first used autocorrelation to search for periodicity, rather than methods related to
Fourier transforms (e.g. periodograms). The motivation being that an individual transit
event may be followed by another some number of days later, and perhaps repeat a few
times, but other similarly (but not exactly) separated events may happen years later or
earlier with a phase that is totally different. We therefore used the discrete
autocorrelation function (DACF) proposed by \citet{1988ApJ...333..646E}, though do not
include uncertainties on individual measurements. For a time series with measurements
$a_i$ at times $t_i$ the DACF first computes the mean $\bar{a}$ from the light curve,
here we used the sigma-clipped mean to remove the dimming events. Then for each pair of
points $a_i$, $a_j$ (with $i\ne j$) computes
$U_{ij}=((a_i-\bar{a})(a_j-\bar{a}) / \sigma_a$, with each $U_{ij}$ associated with a
time lag $\Delta t_{ij}=t_j - t_i$. A series of time lags centered at times $t_{rm lag}$
with width $\Delta t_{\rm lag}$ are then used as bins, and the average in each bin is the
DACF. The DACF is not computed for lag bins with no data. The units of the DACF are
standard deviations of the light curve $\sigma_a$ (again calculated using sigma
clipping).

@@

We found a weak periodic signal near 60-70 days, but neither of the methods described
above show compelling evidence that the dimming events seen towards RZ~Psc are periodic
and not random. While we presented results for single seasons' data, we saw no evidence
for periodicity on longer periods. Aside from the 12 year variation, no periodicity has
been seen in the past \citep{2013A&A...553L...1D}. These searches used periodograms,
which are sensitive to variations with fixed phase and poorly motivated, so we explored
autocorrelation and a similar method. That we found a possible signal can be attributed
to both a different method, and the significantly better temporal coverage of the WASP
and KELT-North data.

@@

Given the possible evidence for 60-70 day periodicity, the location of the occulting
bodies could be relatively close to the star, with semi-major axes of about 0.3au. This
distance is comparable to the 0.4au estimated for optically thin dust at 500K
\citep{2013A&A...553L...1D}. To further investigate the location we turn to a different
aspect of the light curves that provides information on the velocity of the occulting
bodies; the gradients. To convert gradients measured in the light curves to velocity and
orbital distance, we first outline a simple model, and then use this model to interpret
the data.

@@

This section considers a simple one-dimensional model (along $x$) of a cloud that dims a
star. The main assumption is that the cloud is larger than the star, and therefore for a
cloud that passes in front of the star from left to right, the vertical ($y$) size of the
cloud can be ignored. Thus, the cloud is a semi-opaque screen or ``curtain'' that dims
the star, a model very similar to previous analyses of related phenomena
\citep[e.g. KH-15D,
J1407,][]{2006ApJ...644..510W,2014MNRAS.441.2845V,2015ApJ...800..126K}.

@@

The simplest case is a star of uniform surface brightness that is occulted by an
optically thick screen that covers the star from $x=-1$ to $u$ (i.e. the units of length
are now $R_\star$). Then $I=1$ and $\tau(x-x_{\rm cl})$ is a step function at $u$ and the
% observed stellar flux is
% \begin{equation}
%   F = 2 \int_{u}^{1} \sqrt{1-x^2} dx
% \end{equation}
% \citep{2006ApJ...644..510W}. The 
fraction of the total stellar flux ($F_\star = \pi$) seen is
\begin{equation}
  f = F/F_\star = (cos^{-1}[u] - u\sqrt{1-u^2})/\pi
\end{equation}
\citep{2006ApJ...644..510W}, where $f$ has the same units as our normalised light
curve. If the curtain is not completely optically thick then the fraction is instead
\begin{equation}
 f = F/F_\star + (1-F/F_\star)(1-\tau)
\end{equation}

@@

In Figure \ref{fig:sma} we have converted the gradients into semi-major axes using
equation (\ref{eq:acl}). The dashed line shows the stellar radius, estimated to be
approximately Solar based on an age of 25Myr \citep{2013AstL...39..776P} and an effective
temperature of 5350K \citep{2014A&A...563A.139P} using \citet{2000A&A...358..593S}
isochrones. This Figure also includes solid lines of constant gradient, computed using
equation (\ref{eq:acl}) and $f_{\rm min} = 1-\tau$.

@@

\section*{Acknowledgments}

@@

We have no competing interests.

@@

\bibliography{../ref} \bibliographystyle{apj}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{rsos}
\usepackage{hyperref,aas_macros}

@@

\author[Grant M. Kennedy et al]{Grant M. Kennedy$^1$,
  Matthew A. Kenworthy$^2$,
  Joshua Pepper$^3$,
  Joseph E. Rodriguez$^{4,5}$, 
  Robert J. Siverd$^6$, \&
  Keivan G. Stassun$^{5,7}$}

\address{\footnotesize{$^1$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3
  0HA, UK \\
  $^2$ Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the
  Netherlands \\
  $^3$ Department of Physics, Lehigh University, 16 Memorial Drive East, Bethlehem, PA
  18015, USA \\
  $^4$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, MS-78, Cambridge, MA
  02138, USA \\
  $^5$ Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center,
  Nashville, TN 37235, USA \\
  $^6$ Las Cumbres Observatory Global Telescope Network, 6740 Cortona Dr., Suite 102, Santa
  Barbara, CA 93117, USA \\
  $^7$ Department of Physics, Fisk University, 1000 17th Avenue North, Nashville, TN
  37208, USA \\
}}

\subject{astrophysics, extrasolar planets, stars}

\keywords{variable stars, protoplanetary disks, debris disks, circumstellar matter}

\corres{Grant M. Kennedy \\
\email{gkennedy@ast.cam.ac.uk}}

\begin{fmtext}
\end{fmtext}

@@

\maketitle

@@

Disks of gas and dust surround essentially all young analogues of our Sun
(e.g. \cite{2001ApJ...553L.153H}). The lifetime of the gas in these disks is very short
compared to the stellar lifetime, and within a few million years most has accreted onto
the star and the remainder been lost to space in photoevaporative flows. The evolution of
the dust during this phase is uncertain, but the existence of gas giant planets makes it
clear that planetary building blocks, and of course some planets, form on a similar or
shorter timescale.

Beyond the first few million years a typical star hosts a planetary system, the
components being the planets themselves and a residual disk of small bodies. These
``planetesimals'' -- the asteroids and comets -- make up the ``debris disk'', where the
standard picture is that destructive collisions between them generate a size distribution
of fragments that extends down to micron-sized dust
(e.g. \cite{1993prpl.conf.1253B,2002MNRAS.334..589W,2010RAA....10..383K}).

The state of planetary systems as they emerge from the gas-rich phase is
uncertain. Planets' locations are not finalised at this epoch, but may move by
interacting with other stars, planets, and/or planetesimals in the system
(e.g. \cite{2007ApJ...669.1298F,1996Sci...274..954R,2005Natur.435..459T}). Similarly, the
state and origin of the debris disk is uncertain. At stellocentric distances near 1au,
the region of interest in this article, it could be that dust observed at this time is
related to the final stages of planet formation
(e.g. \cite{2010ApJ...717L..57M,2012MNRAS.425..657J}), originates in young analogues of
our Asteroid belt \cite{2013MNRAS.433.2334K}, is a signature of comets scattered inwards
from more distant regions (e.g. \cite{2009MNRAS.399..385B}), or is simply a remnant of
the gas-rich disk that has yet to be dispersed \cite{2014MNRAS.438.3299K}. In the absence
of gas detections that argue for the latter scenario, discerning among these various
scenarios, which are not mutually exclusive, is difficult.

A promising way to probe these inner regions is by observing temporal variability
(e.g. \cite{2014Sci...345.1032M}). Optical and IR stellar variation has been studied
for decades (e.g. \cite{1945ApJ...102..168J,1994AJ....108.1906H}), and has recently
been reinvigorated by large scale efforts
(e.g. \cite{2011ApJ...733...50M,2014AJ....147...82C}) and as a side-effect of
large-scale surveys for transiting planets
\cite{2012AJ....143...72M,2013AJ....146..112R,2016MNRAS.457.3988B}. Of many different
classes of variables, the ones of most interest and relevance here are the
``UXOrs''. These are usually Herbig Ae/Be stars, and typically show several magnitudes of
extinction that is generally attributed to variable obscuration by circumstellar dust
\cite{1994AJ....108.1906H,1999AJ....118.1043H,2000A&A...364..633N}.\footnote{Not all
  stars occulted by dust are UXOrs. Two main classes are: those occulted by circumstellar
  material beyond $\gtrsim$10au, such as AA~Tau and V409~Tau which show
  $\gtrsim$year-long dimming events \cite{2013A&A...557A..77B,2015AJ....150...32R}, and
  systems such as $\epsilon$~Aur, J1407, EE~Cep, and OGLE-LMC-ECL-11893 where the
  occultations are attributed to circumsecondary disks
  (e.g. \cite{1999MNRAS.303..521M,2012AJ....143...72M,2014ApJ...788...41D,2015ApJS..220...14K}).}
Two key arguments that favour circumstellar dust as the cause are i) ``blueing'', where
the star is reddened when moderately dimmed but returns to the stellar colour for very
deep ($\gtrsim$1mag) events -- the remaining flux is interpreted as light scattered off
circumstellar dust \cite{1988SvAL...14...27G}, and ii) increased polarisation fraction
during dimming events, caused by a greater fraction of the flux being contributed by
dust-scattered light (e.g. \cite{2001ARep...45...51R}). UXOrs therefore reveal
information on the degree of non-axisymmetry, the ``clumpiness'', of dust orbiting a star
on spatial scales similar to the star itself. The observations can span multiple orbits
to test for repeated dimming events (e.g. \cite{1999A&A...349..619B}), and by using
different bandpasses and polarisation can estimate dust grain sizes
(e.g. \cite{1988SvAL...14...27G,1994ASPC...62...63G}).

In the majority of UXOr-like cases (i.e. those related to obscuration by dust), including
other classes such as ``dippers''
(e.g. \cite{2014AJ....147...82C,2016ApJ...816...69A}), the processes causing young
stars to vary are attributed to gas-rich protoplanetary disks. For Herbig Ae/Be stars the
obscuration is thought to be caused by hydrodynamic turbulence that lifts dust above the
puffed up inner rim of a self-shadowed disk \cite{2003ApJ...594L..47D}. For the dippers,
which are observed around low-mass stars, the obscuration is attributed to dust in
accretion streams that link the inner disk and the stellar surface, and/or to variations
in the height of the inner disk edge
\cite{1999A&A...349..619B,2016ApJ...816...69A,2016arXiv160503985B}. The common theme is
therefore that the location of the occulting dust is as close to the star as physically
possible, being set by sublimation. These systems tell us about the nature of turbulence
and accretion in gas-dominated disks, but so far reveal little about how these disks
transition to the debris phase and the subsequent evolution.

Here we focus on RZ~Psc, a star that shows UXOr-like variability
(e.g. \cite{1985PZ.....22..181Z,1999A&AS..140..293G,2003ARep...47..580S}). As a young
K0V type star with no evidence for gas accretion, but a strong infrared (IR) excess
suggestive of an Asteroid belt analogue, this system appears unique among UXOrs and may
provide new information on the structure of inner planetary systems following dispersal
of the gas disk \cite{2010A&A...524A...8G,2013A&A...553L...1D}. Specifically, we use a
decade of ground-based optical photometry of RZ~Psc (section \ref{s:data}) to draw
conclusions on dust location (section \ref{s:where}), and discuss the possible disk
structure and evolutionary state in section \ref{s:disk}. We conclude in section
\ref{s:conc}.

@@

There is significant evidence that the optical variations seen towards RZ~Psc are caused
by circumstellar dust: i) during dimming events the colour becomes redder
\cite{1985PZ.....22..181Z,1980PZ.....21..310K} in a way consistent with that expected for
dust \cite{1981Afz....17...87P,2004ARep...48..470P}, ii) the maximum depth is about
2.5mag and during these events the colour returns to near stellar values, suggesting that
the remaining emission is from light scattered off the circumstellar dust (i.e. the star
is fully occulted \cite{1981Afz....17...87P,1988SvAL...14...27G}, and iii) the
polarisation fraction increases during the transits, as expected if an increasing
fraction of the light is scattered off circumstellar dust
\cite{1988SvAL...14...27G,1991Afz....34..333K,2003ARep...47..580S}.

What separates RZ~Psc from other UXOrs (and dippers) is i) the spectral type is K0V
rather than Herbig Ae/Be for UXOrs and M-type for dippers, ii) the occulting dust lies
well beyond the sublimation radius, and iii) the star is not associated with a
star-forming region so is inferred to be a few tens of millions of years old. The dust
distance has been inferred from the speed of ingress of dimming events, which was
previously estimated as about 0.6au (for circular orbits
\cite{2013A&A...553L...1D}). Corroborating evidence comes from the $\sim$500K temperature
of the dust seen in the mid-IR, which places it near 0.4-0.7au (depending on optical
depth) and therefore at a location consistent with the occulting dust
\cite{2013A&A...553L...1D}. The distance to RZ~Psc is unknown, but as an apparently
isolated star that shows Li absorption the age has been estimated as a few tens of Myr,
and therefore beyond the age at which a gas-rich disk should exist
\cite{2010A&A...524A...8G,2014A&A...563A.139P}. Further distinguishing features are that
the duration of the dimming events is relatively short compared to other UXOrs, a few
days rather than a few weeks, and that no near-IR excess or accretion signatures are seen
\cite{2014A&A...563A.139P}, so interpretations related to accretion of disk material onto
the star (e.g. \cite{1999AJ....118.1043H,1999A&A...349..619B,2016arXiv160503985B}) are
unlikely.

Thus, the potentially compelling and unique aspect for RZ~Psc is that we are observing
dimming events from dust in a main-sequence planetary system that resides at about
0.5au. This dust is also seen in thermal emission, so deriving joint constraints on the
dust properties and structure may be possible. As argued by \cite{2013A&A...553L...1D} a
picture is emerging in which RZ~Psc is surrounded by a massive young version of our own
asteroid belt, in which planetesimals are continually being destroyed. These collisions
generate the large collective surface area of small dust that emits strongly in the
mid-IR, and the system geometry means that this dust also sometimes passes in front of
the star.

Given an interpretation related to individual planetesimal disruptions, rather than
hydrodynamics, it is perhaps surprising that to date the dimming events are not seen to
be periodic \cite{1999AstL...25..243R,2013A&A...553L...1D}. The only cyclical variation
seen in light curves for RZ~Psc is a 12.4 year variation with an amplitude of 0.5 mag,
which is attributed to either a magnetic cycle, or precession of an otherwise unseen
outer disk due to perturbations from an unseen companion \cite{2013A&A...553L...1D}.

@@

To study the temporal variability of RZ~Psc we use two seasons of public data from the
Wide-Angle Search for Planets (WASP \cite{2006PASP..118.1407P}), and nine seasons of data
from the Kilodegree Extremely Little Telescope North (KELT-North
\cite{2007PASP..119..923P}. We also collected, but ultimately did not use, photometric
observations of RZ~Psc from a wide variety of other sources
(\cite{1994AJ....108.1906H,1973IBVS..783....1K,1980PZ.....21..310K,1985PZ.....22..181Z,1991Afz....34..333K,1997AcA....47..467P,2014Ap.....57..491P},
the Catalina Sky Survey, the American Association of Variable Star Observers, the All-Sky
Automated Survey). Most of these other data have been previously published and their
collation here is largely for the benefit of others. This compilation contains nearly all
data for which tables have been published, but aside from the Harvard plate photometry
published by \cite{1999A&AS..140..293G} we have not sought other photometry so the light
curve remains incomplete.\footnote{Normalised photometry is available at
  \href{https://github.com/drgmk/rzpsc}{https://github.com/drgmk/rzpsc}}

Here we focus on the WASP and KELT-North data, as it has not been previously analysed and
has considerably higher cadence (many measurements per night) and temporal coverage
(nightly, weather permitting) than other data sets. The WASP data from 2004 and 2006 are
public and were obtained from an online
archive\footnote{\href{http://wasp.cerit-sc.cz}{http://wasp.cerit-sc.cz}}. These data
were processed in a manner similar to that described by \cite{2014MNRAS.441.2845V},
where common-mode variations were removed using 50 quiet nearby stars. The KELT-North
data, 2006-2014, were used in raw form, the only specific treatment being a 4\% relative
correction being made to ensure observations taken in the ``east'' and ``west'' telescope
orientations have the same calibration. For a full description of the KELT-North data
reduction, see \cite{2012ApJ...761..123S}.

@@

Nevertheless, Figure \ref{fig:waspkeltzoom} shows an unprecedented view of dimming events
seen towards RZ~Psc, and that key information on the ingress and egress of dimming events
is present. The dimming rate is such that it can be resolved temporally, and hence the
velocity and radial location of the dust clumps estimated. While such estimates have been
made in the past based on one or two individual events \cite{1985PZ.....22..181Z}, these
data make them possible for an ensemble of tens of events.

@@

% period-search.pro
\begin{figure}
\begin{center}
\hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{figs/auto.eps}
\caption{Discrete autocorrelation function for yearly WASP and KELT-North data, computed for
  lags between 10-155 days). The second and third lines from the top show all data, and
  2006-excluded data. Squares show points more than 3$\sigma$ from the sigma-clipped
  mean. The topmost line shows the number of years that show a peak (square) within each
  5 day bin. The peak at 70 days is 7 years and the dashed line is zero.}\label{fig:auto}
\end{center}
\end{figure}

We first used autocorrelation to search for periodicity, rather than methods related to
Fourier transforms (e.g. periodograms). The motivation being that an individual transit
event may be followed by another some number of days later, and perhaps repeat a few
times, but other similarly (but not exactly) separated events may happen years later or
earlier with a phase that is totally different. We therefore used the discrete
autocorrelation function (DACF) proposed by \cite{1988ApJ...333..646E}, though do not
include uncertainties on individual measurements. For a time series with measurements
$a_i$ at times $t_i$ the DACF first computes the mean $\bar{a}$ from the light curve,
here we used the sigma-clipped mean to remove the dimming events. Then for each pair of
points $a_i$, $a_j$ (with $i\ne j$) computes
$U_{ij}=((a_i-\bar{a})(a_j-\bar{a}) / \sigma_a$, with each $U_{ij}$ associated with a
time lag $\Delta t_{ij}=t_j - t_i$. A series of time lags centered at times $t_{rm lag}$
with width $\Delta t_{\rm lag}$ are then used as bins, and the average in each bin is the
DACF. The DACF is not computed for lag bins with no data. The units of the DACF are
standard deviations of the light curve $\sigma_a$ (again calculated using sigma
clipping).

@@

We found a weak periodic signal near 60-70 days, but neither of the methods described
above show compelling evidence that the dimming events seen towards RZ~Psc are periodic
and not random. While we presented results for single seasons' data, we saw no evidence
for periodicity on longer periods. Aside from the 12 year variation, no periodicity has
been seen in the past \cite{2013A&A...553L...1D}. These searches used periodograms,
which are sensitive to variations with fixed phase and poorly motivated, so we explored
autocorrelation and a similar method. That we found a possible signal can be attributed
to both a different method, and the significantly better temporal coverage of the WASP
and KELT-North data.

@@

Given the possible evidence for 60-70 day periodicity, the location of the occulting
bodies could be relatively close to the star, with semi-major axes of about 0.3au. This
distance is comparable to the 0.4au estimated for optically thin dust at 500K
\cite{2013A&A...553L...1D}. To further investigate the location we turn to a different
aspect of the light curves that provides information on the velocity of the occulting
bodies; the gradients. To convert gradients measured in the light curves to velocity and
orbital distance, we first outline a simple model, and then use this model to interpret
the data.

@@

This section considers a simple one-dimensional model (along $x$) of a cloud that dims a
star. The main assumption is that the cloud is larger than the star, and therefore for a
cloud that passes in front of the star from left to right, the vertical ($y$) size of the
cloud can be ignored. Thus, the cloud is a semi-opaque screen or ``curtain'' that dims
the star, a model very similar to previous analyses of related phenomena (e.g. KH-15D,
J1407 \cite{2006ApJ...644..510W,2014MNRAS.441.2845V,2015ApJ...800..126K}).

@@

The simplest case is a star of uniform surface brightness that is occulted by an
optically thick screen that covers the star from $x=-1$ to $u$ (i.e. the units of length
are now $R_\star$). Then $I=1$ and $\tau(x-x_{\rm cl})$ is a step function at $u$ and the
% observed stellar flux is
% \begin{equation}
%   F = 2 \int_{u}^{1} \sqrt{1-x^2} dx
% \end{equation}
% \cite{2006ApJ...644..510W}. The 
fraction of the total stellar flux ($F_\star = \pi$) seen is
\begin{equation}
  f = F/F_\star = (cos^{-1}[u] - u\sqrt{1-u^2})/\pi
\end{equation}
\cite{2006ApJ...644..510W}, where $f$ has the same units as our normalised light
curve. If the curtain is not completely optically thick then the fraction is instead
\begin{equation}
 f = F/F_\star + (1-F/F_\star)(1-\tau)
\end{equation}

@@

In Figure \ref{fig:sma} we have converted the gradients into semi-major axes using
equation (\ref{eq:acl}). The dashed line shows the stellar radius, estimated to be
approximately Solar based on an age of 25Myr \cite{2013AstL...39..776P} and an effective
temperature of 5350K \cite{2014A&A...563A.139P} using \cite{2000A&A...358..593S}
isochrones. This Figure also includes solid lines of constant gradient, computed using
equation (\ref{eq:acl}) and $f_{\rm min} = 1-\tau$.

@@

\ack{}

@@

We declare that we have no competing interests.

@@

%\bibliography{../ref} \bibliographystyle{vancouver}

\begin{thebibliography}{10}

\bibitem{2001ApJ...553L.153H}
{Haisch} KE Jr, {Lada} EA, {Lada} CJ.
\newblock {Disk Frequencies and Lifetimes in Young Clusters}.
\newblock \apjl. 2001 Jun;553:L153--L156.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2001ApJ...553L.153H}.
